Kernel Phase and Coronagraphy with Automatic Differentiation

### 2020-05-28 ms.tex

>>>>

\begin{figure}
\plotone{comparison_posterior_sim.pdf}
\caption{Comparison of \citet[][blue stars]{martinache20} and autodiff (orange dots) kernel phase pipelines on simulated data with true parameters $\rho = 125$~mas, $\theta = 86^\circ$, $c=25$. We generate a cube of 1000 mock datasets using a 64-pix pupil model, and the observables used are the median and standard error of the mean of each kernel phase across this ensemble. Both datasets retrieve the true parameters very precisely, though with small systematic offsets, which are slightly larger for the autodiff method than for classic kernel phases. \label{method_comparison_ensemble}}
\end{figure}

\begin{figure}
\plotone{comparison_posterior_sim.pdf}
\caption{Comparison of \citet[][blue stars]{martinache20} and autodiff (orange dots) kernel phase pipelines on simulated data with true parameters $\rho = 125$~mas, $\theta = 86^\circ$, $c=25$. We generate a cube of 1000 mock datasets using a 64-pix pupil model, and the observables used are the median and standard error of the mean of each kernel phase across this ensemble. Both methods retrieve the true parameters very precisely, though with small systematic offsets, which are slightly larger for the autodiff method than for classic kernel phases. \label{method_comparison_ensemble}}
\end{figure}

\begin{figure}
\plotone{comparison_posterior_sim_cube.pdf}
\caption{Comparison of \citet[][blue stars]{martinache20} and autodiff (orange dots) kernel phase pipelines on simulated data with true parameters $\rho = 125$~mas, $\theta = 86^\circ$, $c=25$. We generate a cube of 1000 mock datasets using a 64-pix pupil model and Zernike aberrations as described in Section~\ref{sec:palomar}. The corner plot displays the parameters retrieved using a simple least squares fit applied to each individual frame. The methods have very similar distributions centred tightly on the true value, though there are more outliers in the autodiff implementation. \label{method_comparison_ensemble}}
\end{figure}
